---
title: "BIO-assinment"
author: "JOJO"
date: "August 31, 2018"
output: html_document

2. Read the .xlsx file and .csv file into R, and create 3 data.frame objects.
```{r}
library(readxl)
dataset <- read_excel("dataset.xlsx")
View(dataset)
library(readr)
metadata <- read_csv("metadata.csv")
View(metadata)
identifier <- c("0.94_431.39","5.58_232.15","3.12_311.16","0.94_552.43","1.06_225.20","7.20_282.12","6.08_137.07","6.66_120.08","1.35_168.07","4.96_137.05","1.36_134.06","1.71_273.11","1.22_136.08","7.40_156.08","3.49_424.34","1.29_176.07","1.48_785.59","1.18_131.07","1.36_204.11","6.65_158.12","1.36_110.07","2.62_121.03","3.99_139.05","1.22_144.05","4.69_94.06","1.85_147.09","0.98_369.35","6.35_258.11","1.24_431.32","1.35_152.07","1.46_232.03","6.99_204.12","1.32_189.10","2.91_268.18","1.68_360.36","1.72_332.33","7.03_118.09","2.57_240.11","1.24_195.09","5.18_104.11","2.50_325.17","1.22_347.22","1.28_361.20","1.55_177.10","4.95_114.07","4.32_316.25","4.65_302.31","7.56_230.09","8.72_293.10","1.75_298.35","5.91_466.32","4.92_260.19","1.41_363.22","4.01_256.11_4.00_238.10","1.08_263.08","1.23_190.09","6.68_209.09_6.68_192.07","4.07_344.28","7.54_184.09","6.19_218.14","5.51_268.15","1.01_357.30","1.19_602.21","7.08_144.10","5.48_312.13","1.23_296.07","1.79_123.07","1.08_152.07","7.01_130.09","1.01_520.51","2.30_153.07","4.59_288.22","1.02_282.28","3.38_426.36","1.16_362.12","1.47_378.11","3.53_400.34","4.35_780.55","3.82_220.12","5.78_265.12_5.78_287.10","6.66_166.09_6.66_149.06","1.04_286.14","4.20_264.20","3.14_168.06_3.14_242.13","5.71_177.10_5.71_160.08","1.39_198.06","6.88_182.06_6.89_144.10","3.34_428.37","1.14_254.06","5.95_516.30","5.47_76.08","1.00_340.10","6.44_150.11","7.25_138.05","4.53_291.15","6.62_205.10_6.62_188.07","7.46_182.08","2.99_61.04")
Annotation <- c("(+)-.alpha.-Tocopherol","(R)-Butyrylcarnitine","(S)-Desmethylcitalopram",".beta.-Cryptoxanthin","1,3-Dicyclohexylurea","1-Methyladenosine","1-Methylnicotinamide","2-Amino-1-phenylethanol","2-Amino-3-methoxybenzoic  acid","2'-Deoxyinosine","2-Indolinone","2'-o-Methyl-5-methyluridine","2-Phenylacetamide","3-(1-Pyrazolyl)-alanine","3-Hydroxyoleylcarnitine","3-Indoleacetic acid","3-Ketopetromyzonol","4-Acetylbutyric acid","4-Aminoantipyrine","4-Aminomethylcyclohexanecarboxylic acid","4-Aminophenol","4-Hydroxybenzoic acid","4-Imidazoleacrylic acid","4-Methyl-5-thiazoleethanol","4-Picoline","5,6-Dimethylbenzimidazole","5.alpha.-Cholest-7-en-3.beta.-ol","5-Methylcytidine","7.alpha.-Hydroxy-3-oxo-4-cholestenoic acid","Acetaminophen","Acetaminophen sulfate","Acetylcarnitine","Antipyrine","Auramine O","Benzyldimethylstearylammonium cation","Benzyldimethyltetradecylammonium cation","Betaine","Bupropion","Caffeine","Choline","Citalopram","Corticosterone","Cortisone","Cotinine","Creatinine","Decanoyl-L-carnitine","Dihydrosphingosine B","Ergothioneine","Ethylenediaminetetraacetic acid","Ethylhexadecyldimethylammonium cation","Glycocholic acid","Hexanoyl-L-carnitine","Hydrocortisone","Hydroxybupropion","Indirubin","Indole-3-propionic acid","Kynurenine","Lauroyl-L-carnitine","L-Carnitine","L-Propionylcarnitine","Metoprolol acid","Monoolein","Montelukast-1,2-diol","N.alpha.-Methyl-L-lysine","N2,N2-Dimethylguanosine","N-Acetylsulfamethoxazole","Nicotinamide","N-Methylanthranilic acid","N-Methylproline","N-Palmitoyl-D-sphingosine","Nudifloramide","Octanoylcarnitine","Oleamide","Oleoyl-L-carnitine","Omeprazole sulfone","OmeprazoleTABsulfone N-oxide","Palmitoylcarnitine","Palmitoyleicosapentaenoyl phosphatidylcholine","Pantothenic acid","Phenylacetyl-L-glutamine","Phenylalanine","Piperine","R-(-)-O-Desmethylvenlafaxine","racTABerythro-Dihydrobupropion","Serotonin","S-Methyl-3-thioacetaminophen","Stachydrine","Stearoyl-L-carnitine","Sulfamethoxazole","Taurocholic acid","TMAO","Topiramate","Triethanolamine","Trigonelline","Trimethoprim","Tryptophan","Tyrosine","Urea")			
InChi <- c("GVJHHUAWPYXKBD-IEOSBIPESA-N","QWYFHHGCZUCMBN-SECBINFHSA-N","PTJADDMMFYXMMG-IBGZPJMESA-N","DMASLKHVQRHNES-FKKUPVFPSA-N","ADFXKUOMJKEIND-UHFFFAOYSA-N","GFYLSDSUCHVORB-IOSLPCCCSA-N","LDHMAVIPBRSVRG-UHFFFAOYSA-O","ULSIYEODSMZIPX-UHFFFAOYSA-N","SXOPCLUOUFQBJV-UHFFFAOYSA-N","VGONTNSXDCQUGY-JXBXZBNISA-N","JHFAEUICJHBVHB-UHFFFAOYSA-N","YHRRPHCORALGKQ-FDDDBJFASA-N","LSBDFXRDZJMBSC-UHFFFAOYSA-N","PIGOPELHGLPKLL-YFKPBYRVSA-N","YBCVTTMMURGSEY-LMLDZDDJSA-N","SEOVTRFCIGRIMH-UHFFFAOYSA-N","WKLORKLFLMTHHY-RTYFXBAISA-N","MGTZCLMLSSAXLD-UHFFFAOYSA-N","RLFWWDJHLFCNIJ-UHFFFAOYSA-N","GYDJEQRTZSCIOI-LJGSYFOKSA-N","PLIKAWJENQZMHA-UHFFFAOYSA-N","FJKROLUGYXJWQN-UHFFFAOYSA-N","LOIYMIARKYCTBW-OWOJBTEDSA-N","BKAWJIRCKVUVED-UHFFFAOYSA-N","FKNQCJSGGFJEIZ-UHFFFAOYSA-N","LJUQGASMPRMWIW-UHFFFAOYSA-N","IZVFFXVYBHFIHY-FTTZNKGKSA-N","ZAYHVCMSTBRABG-JXOAFFINSA-N","SATGKQGFUDXGAX-SLTBQWEQSA-N","RZVAJINKPMORJF-UHFFFAOYSA-N","IGTYILLPRJOVFY-UHFFFAOYSA-N","RDHQFKQIGNGIED-MRVPVSSYSA-O","VEQOALNAAJBPNY-UHFFFAOYSA-N","JPIYZTWMUGTEHX-UHFFFAOYSA-N","FWLORMQUOWCQPO-UHFFFAOYSA-N","WNBGYVXHFTYOBY-UHFFFAOYSA-N","KWIUHFFTVRNATP-UHFFFAOYSA-N","SNPPWIUOZRMYNY-UHFFFAOYSA-N","RYYVLZVUVIJVGH-UHFFFAOYSA-N","OEYIOHPDSNJKLS-UHFFFAOYSA-N","WSEQXVZVJXJVFP-UHFFFAOYSA-N","OMFXVFTZEKFJBZ-HJTSIMOOSA-N","MFYSYFVPBJMHGN-ZPOLXVRWSA-N","UIKROCXWUNQSPJ-VIFPVBQESA-N","DDRJAANPRJIHGJ-UHFFFAOYSA-N","LZOSYCMHQXPBFU-OAHLLOKOSA-N","OTKJDMGTUTTYMP-UHFFFAOYSA-N","SSISHJJTAXXQAX-ZETCQYMHSA-N","KCXVZYZYPLLWCC-UHFFFAOYSA-N","VCAVAURZPNANDQ-UHFFFAOYSA-N","RFDAIACWWDREDC-FRVQLJSFSA-N","VVPRQWTYSNDTEA-LLVKDONJSA-N","JYGXADMDTFJGBT-VWUMJDOOSA-N","RCOBKSKAZMVBHT-UHFFFAOYSA-N","CRDNMYFJWFXOCH-BUHFOSPRSA-N","GOLXRNDWAUTYKT-UHFFFAOYSA-N","YGPSJZOEDVAXAB-QMMMGPOBSA-N","FUJLYHJROOYKRA-QGZVFWFLSA-N","PHIQHXFUZVPYII-UHFFFAOYSA-N","UFAHZIUFPNSHSL-MRVPVSSYSA-N","PUQIRTNPJRFRCZ-UHFFFAOYSA-N","RZRNAYUHWVFMIP-KTKRTIGZSA-N","UFQIEVSCRCMNLW-SHISVWIYSA-N","OLYPWXRMOFUVGH-LURJTMIESA-N","RSPURTUNRHNVGF-IOSLPCCCSA-N","GXPIUNZCALHVBA-UHFFFAOYSA-N","DFPAKSUCGFBDDF-UHFFFAOYSA-N","WVMBPWMAQDVZCM-UHFFFAOYSA-N","CWLQUGTUXBXTLF-YFKPBYRVSA-N","YDNKGFDKKRUKPY-TURZORIXSA-N","JLQSXXWTCJPCBC-UHFFFAOYSA-N","CXTATJFJDMJMIY-CYBMUJFWSA-N","FATBGEAMYMYZAF-KTKRTIGZSA-N","IPOLTUVFXFHAHI-WHIOSMTNSA-N","IXEQEYRTSRFZEO-UHFFFAOYSA-N","ZBGMHRIYIGAEGJ-UHFFFAOYSA-N","XOMRRQXKHMYMOC-UHFFFAOYSA-N","KLTHQSWIRFFBRI-KOQZQRJKSA-N","GHOKWGTUZJEAQD-UHFFFAOYSA-N","RCOBKSKAZMVBHT-UHFFFAOYSA-N","COLNVLDHVKWLRT-QMMMGPOBSA-N","MXXWOMGUGJBKIW-YPCIICBESA-N","KYYIDSXMWOZKMP-HNNXBMFYSA-N","NDPTTXIBLSWNSF-BXKDBHETSA-N","QZAYGJVTTNCVMB-UHFFFAOYSA-N","KNDKLDWGYWQCCJ-UHFFFAOYSA-N","CMUNUTVVOOHQPW-UHFFFAOYSA-N","FNPHNLNTJNMAEE-HSZRJFAPSA-N","JLKIGFTWXXRPMT-UHFFFAOYSA-N","WBWWGRHZICKQGZ-HZAMXZRMSA-N","UYPYRKYUKCHHIB-UHFFFAOYSA-N","KJADKKWYZYXHBB-XBWDGYHZSA-N","GSEJCLTVZPLZKY-UHFFFAOYSA-N","WWNNZCOKKKDOPX-UHFFFAOYSA-N","IEDVJHCEMCRBQM-UHFFFAOYSA-N","QIVBCDIJIAJPQS-VIFPVBQESA-N","OUYCCCASQSFEME-QMMMGPOBSA-N","XSQUKJJJFZCRTK-UHFFFAOYSA-N")
species <- c("[M+H]+","[M+H]+","[M+H]+","[M]+.","[M+H]+","[M+H]+","[M+H]+","[M+H-H2O]+","[M+H]+","[M+H-C5H8O3]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H-H2O]+","[M+H]+","[2M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H-H2O]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H-H2O]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[Cat-C2H4]+","[Cat]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[Cat]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+_[M+H-H2O]+","[M+H]+","[M+H]+","[M+H]+_[M+H-NH3]+","[M+H]+","[M+Na]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H-NH3]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H-H2O]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+_[M+Na]+","[M+H]+_[M+H-NH3]+","[M+H]+","[M+H]+","[M+H]+_[M+H-C410O]+","[M+H]+_[M+H-NH3]+","[M+H]+","[M+H]+_[M+K]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+","[M+H]+_[M+H-NH3]+","[M+H]+","[M+H]+")
count <- c("80","80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80"," 80","EMPTY","-1","853.6538","915.7516","899.5435","757.31 804","92 80.68 804","955.3895","963.1943","-1","-1","-1","896.5677","948.47 806","972.7356","-1","865.4886")	
ESI <- c("ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","ESI(+)","EMPTY","-1","862.298","946.2116","966.1121","895.1586","934.7672","955.3894","981.4338","-1","-1","-1","892.2752","908.7713","980.6624","EMPTY","-1","873.4531")
mean <- c("6685","7701","110","15025","7009","2273","6152","25695","132","1784","3216","599","385","304","12132","1353","963","180","222","3012","532","102","5090","18","653","127","139491","42","7438","4282","2372","124871","199","77","18597","21185","396733","128","22517","68577","120","253","1526","28919","265392","884","607","96","2085","1484","1293","1197","8133","397","739","545","2593","1800","17091","14362","80","5050","18","2163","605","69","11199","675","6720","6650","39427","2409","10038","13363","31","28","10564","165642","2640","8561","31654","34303","73","314","257","117","341741","4490","12","105","4944","765","1658","8206","55","73383","2247","58631")																																																																																											
CV <- c("25","10","17","12","22","11","9","14","30","10","8","29","15","61","12","18","15","12","23","20","97","21","91","51","13","29","11","21","8","14","5","11","26","20","246","246","8","14","14","18","32","16","39","14","11","20","15","27","218","72","15","11","11","17","70","19","11","21","14","10","39","8","28","13","32","44","40","134","9","12","12","10","41","14","35","34","10","7","6","27","12","9","45","23","21","51","8","14","43","19","19","35","34","15","32","12","14","5")

mz <- c("431.3863","232.1543","311.1551","552.4321","225.1959","282.1194","137.0702","120.0803","168.0655","137.0453","134.0596","273.112","136.0751","156.0764","424.3416","176.0703","785.5925","131.0712","204.1136","158.117","110.0679","121.0285","139.05","144.0469","94.065","147.0915","369.3517","258.1078","431.3153","152.071","232.0276","204.1236","189.1017","268.1802","360.3623","332.331","118.0864","240.113","195.088","104.1069","325.1719","347.2237","361.2","177.1024","114.0664","316.2481","302.305","230.0894","293.098","298.3467","466.3162","260.1852","363.2161","256.11_238.0995","263.0815","190.0866","209.0918_192.0651","344.2794","184.094","218.1385","268.1546","357.2988","602.2132","144.1013","312.1301","296.0725","123.0652","152.071","130.0859","520.5083","153.0656","288.2168","282.2796","426.357","362.1153","378.1097","400.3416","780.5538","220.1177","265.1185_287.0999","166.0861_149.0593","286.1441","264.1959","168.057_242.1306","177.1022_160.0751","198.0579","182.0576_144.1021","428.3723","254.0603","516.2993","76.0755","340.1018","150.1121","138.0545","291.1456","205.0968_188.0708","182.08","61.0403")
SD <- c("1690","751","19","1862","1558","239","554","3480","40","185","255","172","59","186","1481","243","145","22","50","615","517","22","4645","9","86","37","15504","9","627","587","117","14160","52","15","45825","52038","31468","18","3237","12172","38","40","591","3934","28371","181","93","26","4537","1061","190","136","857","67","517","105","277","387","2401","1393","32","419","5","271","193","31","4437","906","575","798","4906","251","4153","1831","11","10","1106","12295","159","2334","3876","3256","33","74","53","60","28036","623","5","20","937","271","562","1266","18","9144","319","2763")
y <- data.frame(identifier,Annotation,InChi,species,count,ESI,mz,mean,SD,CV)
y
ooneA <- c(58848,14753,93,15204,69743,3208,4509,38528,84,1311,2474,9597,472,70,28538,2525,1660,116,119,5031,202,100,3977,28,563,179,189703,47,19440,1916,222,477646,123,99,3977,5845,413091,116,44547,74417,87,233,1653,3039,248771,7044,211,68,373,776,1315,8387,8217,271,274,1311,3239,9576,26057,36629,94,670,14,3984,893,30,19254,748,488,10619,29778,24125,239200,49129,27,46,35852,282908,1968,21085,46388,6714,59,210,2661,119,7663,8937,20,111,6326,577,976,8746,30,92999,2188,60688)
ooneB <- c(60101,19417,90,20946,38507,3872,7308,41908,121,6993,4234,6390,456,138,31809,2553,1971,141,274,8859,114,122,7412,33,1732,114,190567,59,18484,2216,330,573680,175,76,2304,3028,379641,80,141768,66106,92,233,1905,791,279056,6125,326,95,530,2368,1283,9384,11258,228,271,530,3328,9379,28398,45062,77,1186,32,4750,1461,47,18846,1289,709,11695,45589,23338,224634,52476,41,46,36133,385984,2675,28816,50961,43778,88,246,2074,117,20625,10333,52,123,3389,772,3125,58534,63,130082,2185,80978)
ooneC <- c(31993,13992,105,12307,62361,3822,5659,35639,92,5110,2936,7648,396,69,23606,2960,2186,71,115,11765,303,128,3865,18,2021,85,166642,50,17637,338,47,454537,114,83,1619,2182,387571,87,140564,92562,151,114,1083,682,238155,5546,259,92,73,369,8425,7121,5748,222,274,408,3165,10203,25181,37996,90,724,19,3140,1279,43,18415,528,948,10096,31902,16228,162160,38005,28,37,33712,261709,2073,15025,42831,21155,94,242,1929,106,24457,9225,10,342,4889,610,1054,43714,60,113159,1947,65457)
ooneD <- c(68607,16310,105,29414,54175,3717,6116,41101,375,9221,2990,8280,341,281,27643,2744,1305,73,251,17919,120,92,3421,23,1953,109,237718,64,20350,2870,413,546396,179,56,19929,22080,420309,180,153997,75139,86,382,1528,522,264632,6350,147,90,448,9217,699,8624,11025,254,238,246,3556,10863,29311,36394,135,787,18,4305,1035,36,18857,920,3688,12034,43844,26261,365884,52662,37,47,39640,404883,2295,27874,49617,17040,56,243,1743,160,315236,12637,84,114,6176,397,917,36336,92,104320,2254,72201)
otwoA <- c(43981,18169,78,38841,44709,3969,5974,34686,141,2432,7510,7962,364,55,29621,1321,1766,277,147,14200,141,97,5198,28,1357,161,185316,32,12581,381,30,339609,263,123,2511,2698,412735,131,27842,77721,115,364,2176,606,323028,4299,367,133,453,6378,666,5266,12862,187,162,1697,3689,7650,26027,27862,57,747,10,5145,1505,80,24389,1294,1857,9672,38213,20392,230191,42893,51,19,31191,475424,1942,38060,42660,27639,70,417,3374,121,10174,11910,10,135,4063,450,1801,18460,37,82777,1853,86722)

otwoB <- c(61274,19886,86,52918,39631,4222,3896,37914,114,6072,8416,6568,463,74,26117,1847,733,206,199,13567,223,149,3770,18,1655,157,198054,145,10467,447,24,335208,113,57,20752,23113,508758,168,42009,107214,78,479,2045,536,297873,3915,1420,123,512,27964,1195,5867,16629,492,1571,1728,3584,7084,23824,31734,73,423,10,4763,1969,37,68296,2922,750,8555,31536,20668,160070,43155,27,60,35873,368676,2938,48951,47266,32414,73,258,18230,220,44374,14894,10,101,3174,968,2387,28324,84,94067,2203,80368)

otwoC <- c(39163,15633,99,39121,37737,4145,5648,32546,54,1320,7348,6191,307,46,25298,1241,1861,170,371,12206,175,101,4151,27,1623,92,183587,50,10471,149,14,265242,333,79,3545,6435,410973,69,34831,60570,110,645,2984,468,312812,2928,807,159,601,1472,748,4319,14008,190,234,1586,3302,5302,21806,24457,122,636,4.5,4501,1842,19,42988,998,1079,9087,30594,15278,135434,38820,14,42,27662,383569,1864,30050,38200,39020,64,212,9891,117,30255,12674,10,56,3622,625,1128,22403,106,106588,1958,85716)

otwoD <- c(42607,16555,71,57626,35776,4202,3562,35065,208,1393,8383,6560,421,65,34243,1510,1802,146,181,11804,556,63,5176,10,1149,148,163847,51,11554,18203,3753,381047,217,69,2675,3431,543726,104,27177,69056,97,361,3088,362,326297,6929,198,82,347,1199,325,6133,14278,228,277,1304,3417,9561,22121,24449,125,1755,14,5433,1685,38,18702,2095,1849,8077,27873,25336,184952,55013,27,32,37992,425605,2304,43526,41457,19071,38,246,2493,454,195722,14205,20,78,6979,1086,1737,23652,39,83635,2016,83365)

othreeA <- c(41445,13514,94,46883,38199,3623,5958,30596,75,2238,2820,5254,648,340,22162,3152,403,54,2569,14869,350,94,3787,23,1645,104,168256,33,13850,363,62,313096,314,70,1328,1692,449287,94,62228,84609,116,114,1368,294,248754,5119,173,201,22179,1092,2146,6604,7229,215,196,1135,2890,8460,22579,20785,76,515,28,2307,1027,23,18310,631,1757,8921,30835,18541,194576,38591,657,1299,30093,402201,2905,15207,37882,72787,74,204,2714,79,18015,10204,4.5,209,1750,607,1593,26139,42,101188,1317,76525)

othreeB <- c(48064,13484,97,78438,40075,3018,7133,32805,3128,1106,3558,6137,406,550,26924,2229,693,197,247,3420,9337,103,2963,19,1428,132,129815,59,12057,277423,82262,306322,296,61,562,824,450748,135,2611,102737,114,202,1588,817,235678,6075,326,54,641,930,4203,6906,9661,209,293,963,2926,9313,22761,24946,90,579,27,2145,1032,29,26337,2292,6237,7612,19404,27031,148538,33669,40985,12672,28743,284724,2114,33810,39911,58499,43,193,3806,1559,256977,11128,10,104,4717,3901,426,8046,85,81643,2416,83384)

othreeC <- c(28944,14644,131,56746,26822,3430,4051,30678,64,3896,1675,5486,427,59,29172,2195,869,131,250,4234,221,82,8490,19,1206,276,103133,27,13845,281,47,396739,371,84,1997,2885,493131,139,41371,87670,87,300,1728,483,273682,7953,196,112,794,3831,214,8069,11118,253,217,1794,2820,11108,20704,23853,118,605,24,2325,938,47,15074,1941,2546,8730,15498,30979,174178,47940,27,74,31661,274933,2166,22277,37219,12198,37,229,1986,126,131998,12375,4.5,79,3593,481,1270,57900,41,82910,1938,72094)
            othreeD <- c(35135,12595,108,70996,31616,3659,3294,33008,88,1587,2732,6433,425,46,15957,3240,1072,118,131,9882,108,122,3522,147,1065,241,142947,50,8540,957,355,245684,256,92,1713,2110,456303,126,31815,127448,131,159,1644,595,244532,2463,182,142,576,323,1918,4088,8248,257,262,471,2870,5029,22033,26110,86,431,18,2701,1084,65,16167,3054,2318,9670,19694,12579,222646,24291,298,533,20949,323359,2126,34213,38549,63538,61,221,2204,98,253429,7236,20,109,4999,412,1859,35259,115,83939,2032,91986)
          ofourA <- c(51372,12472,153,64276,41130,4322,5109,32065,151,2004,2898,6282,441,417,20802,1351,212,123,392,2949,549,101,3703,30,17121,126,170362,51,10847,357,133,323637,122,66,1586,1578,505971,165,104046,98547,112,165,2664,425,334653,4898,214,158,419,490,1347,3524,12179,159926,1201,757,3454,8726,19029,15540,84,524,23,7434,1469,42,17659,158,1240,9582,32819,15170,184597,40603,37,56,23667,263508,2679,10060,40090,90628,47,14263,2657,179,65830,9448,18,119,5973,803,1681,84968,52,68282,1791,87708)
           ofourB <- c(47309,14756,235,64372,39415,4112,5612,32760,515,9607,3148,6224,376,313,21369,1050,126,141,165,9930,2378,132,3352,18,28820,107,144800,37,11038,22630,8116,509122,265,90,1623,2317,354865,109,150910,85626,86,146,2067,374,310824,2924,704,203,3324,2847,830,4218,12568,108538,681,622,3016,12260,16905,17926,86,628,10,7712,1759,20,28636,369,1630,9552,60921,11690,267594,48642,41,33,31468,324819,2894,18813,39523,18786,98,8052,9102,695,140827,11189,14,94,2246,823,946,56178,44,85113,1508,82410)
           ofourC <- c(54933,15326,113,61255,6953,3989,4343,35092,105,7418,3222,655,163,143,18996,696,313,181,130,3153,986,116,5185,27,13918,94,226714,46,11469,985,237,414860,260,85,3084,4033,391139,773,134138,78670,153,203,2614,623,282167,2915,107,146,959,3121,1772,3785,13739,151144,1576,1410,3001,7550,16594,24812,141,746,23,5823,950,33,5043,277,1656,12524,34081,10080,115200,38296,37,28,22167,469911,2713,25981,41810,34847,112,60290,662,59,55967,7891,9,119,8171,483,2287,32665,51,86926,1871,84996)
            ofourD <- c(67187,18939,63,60090,7853,4311,6079,41972,141,1521,4949,819,231,118,21891,1784,207,118,206,3818,586,181,3267,32,18777,201,272224,2904,13970,2675,1174,349683,297,46,1483,2054,454582,8243,245594,91292,199,83,2946,22881,325203,3458,267,171,423,506,2562,3412,9414,259814,203,757,4506,7536,22044,23697,89,2574,20,7778,1137,37,16789,336,2241,10750,42889,11667,375472,43263,32,37,26832,520956,2175,24727,50078,66627,64,75130,2911,151,102798,10690,14,227,7622,241,3001,117646,49,89171,1996,92085)
            ofiveA <- c(47936,21179,186,50947,35254,3361,6148,31153,118,1177,5702,5987,492,234,22287,1210,354,185,218,4713,218,131,4242,14,2465,113,96904,41,8346,426,34,258738,216,76,2743,3737,403290,104,19139,77773,84,276,1658,712,255033,5242,140,120,720,3478,6036,4704,11128,882,7658,1495,2712,8185,22248,27063,58,1961,4.5,1297,622,56,16140,638,1558,5613,45318,19578,58921,42878,36,23,23939,211966,3751,27844,37200,3237,56,276,954,100,16937,10510,24,1255,1831,1110,1865,16604,72,89456,1957,79785)
            ofiveB <- c(49213,17544,97,56591,31244,3659,6915,31002,99,993,4807,5595,460,32,18650,1778,438,75,129,4660,385,97,6673,2040,2692,359,121926,41,8630,457,60,238485,144,89,1462,1799,470644,141,20819,106453,78,243,1343,341,248814,4955,113,92,28844,494,4651,4084,10337,201,158,1221,2645,8473,18386,21468,59,532,19,4021,1261,55,9048,598,8235,6436,36562,15856,40926,39266,32,37,26159,211913,4392,26493,38607,11242,61,327,2241,73,622165,11946,4.5,647,4780,806,696,33074,53,74608,3227,87584)
            ofiveC <- c(54558,16746,86,59632,35321,3624,7493,33560,163,856,5880,6223,344,142,19061,1344,374,97,204,4429,206,128,5003,27,2140,132,100947,41,8190,316,30,365384,185,85,3638,4550,433834,122,7371,95437,128,176,1631,302,262316,4282,207,135,849,1505,2945,4393,11276,342,337,1863,3182,7450,22282,25974,91,2006,9,1258,774,46,20593,466,1638,4895,37950,16623,136666,38266,37,32,19605,425643,3451,27373,40615,5244,81,212,2820,85,27636,8213,10,496,2408,1275,2466,12894,46,81338,1916,78857)
            ofiveD <- c(54074,17003,103,70398,36479,3560,7730,31074,108,1347,6161,6203,408,199,18943,1170,747,123,199,3702,216,151,6506,18,2286,148,90186,27,11612,254,28,240692,218,89,1676,1952,425875,84,7316,98748,129,214,1777,747,261335,4219,81,155,2921,2190,7837,3842,10761,306,574,1400,2719,8067,18064,22187,107,463,30,3801,957,37,19280,462,10787,4497,48966,15791,139005,39295,42,41,25640,293784,4235,28650,38751,8086,87,232,1744,90,575248,10096,10,1214,1363,2010,2388,21164,42,88516,3444,81079)
            osixA <- c(47969,14615,104,57654,27849,4084,18042,33968,126,1706,7443,5705,347,995,20928,1200,270,106,143,4794,342,110,3907,19,2581,98,119875,41,13725,856,412,237800,191,111,1489,1627,459729,142,26031,78256,90,666,2214,906,307704,5074,326,262,2900,3068,1454,4198,18324,513,251,829,3267,9506,21955,18265,114,466,36,8245,1448,34,22712,603,5895,7345,103240,20968,81888,43093,50,123,25868,684187,5756,45153,41640,10089,51,303,3333,125,448633,8746,28,207,7766,1132,1706,25084,38,91098,2450,92463)
           osixB <- c(50634,15931,78,56228,29165,4832,11764,37286,829,2635,3621,6252,528,277,24266,1229,401,88,94,1182,3585,153,3155,29,2906,113,147064,54,13797,73228,36675,456211,255,147,1704,1821,479940,115,34344,82049,135,417,1850,511,319755,3962,223,214,1481,916,972,4568,15046,578,105,747,3527,8662,24952,23037,104,833,27,7744,1091,33,18990,498,1936,10143,120512,16086,84196,48404,32,51,29320,315856,9843,46654,45083,24000,70,263,2127,670,245633,11242,4.5,106,12266,1008,1935,26736,92,83098,2464,93646)
           osixC <- c(48695,12854,97,58654,28106,4049,5988,28733,113,9468,8114,5357,341,45,22661,1303,292,179,201,12206,561,140,3190,24,6641,112,209448,37,13515,318,63,338381,206,70,2644,4468,546002,221,36108,86239,132,177,1780,516,273789,2523,184,71,16507,510,1320,3482,10282,491,659,1196,3225,7137,19217,16650,83,617,18,8209,979,104,18355,131,2910,11242,57968,10984,175194,43804,33,103,26507,475536,6366,38942,34438,55452,73,252,2735,101,457491,9952,9,184,10337,252,943,22216,29,84128,2381,104876)
            osixD <- c(51781,11964,120,63000,28346,4162,6732,33076,129,1652,5631,6155,341,89,24139,1253,1156,142,221,3661,219,118,4531,18,2427,166,197041,41,13388,365,76,217554,301,57,1967,2829,514782,313,12442,95180,116,666,1931,3277,280696,2931,227,129,545,63877,1353,3156,15789,204,1163,1246,3722,7125,19274,18877,101,558,27,7231,1032,60,19850,279,2153,10058,36911,13024,352043,40258,27,47,25943,266367,5007,35632,39787,32800,85,195,3121,88,254368,10328,10,210,3600,1794,4100,23210,46,83652,2320,93160)
            osevenA <- c(56553,30305,102,41860,32768,3651,4560,28687,90,1309,6122,5310,585,74,21435,1260,615,146,144,3708,161,252,2951,9,1535,145,153022,54,7086,346,10,322912,417,79,759,1520,422651,147,11009,66676,107,255,1623,315,253516,10541,79,122,4298,377,453,8695,16156,258,205,592,3069,12058,21990,22881,33024,353,10,1741,1228,20,15568,430,2345,8135,25582,44411,54222,40961,19,28,28729,237999,3345,27042,34145,24680,102,228,1606,107,44446,10877,20,157,6321,869,1138,14441,84,100044,1555,76783)
            osevenB <- c(59214,26137,107,54633,34294,3102,3833,26317,155,1892,6965,5857,390,94,21456,1228,210,200,214,30781,274,113,4707,18,491,130,203210,59,8422,433,10,235747,239,74,1802,2235,460216,87,10664,86955,116,250,1973,397,235478,5316,121,108,5986,7036,367,6001,16805,331,378,611,2914,6488,21784,24642,6707,454,18,1679,887,50,17071,242,1543,9425,29063,29353,111144,39458,28,41,30336,254825,4991,24932,31077,11184,38,199,1952,90,37352,11818,33,146,6410,556,1379,18564,63,97167,1430,78634)
            osevenC <- c(45821,23173,111,32096,32184,3253,2730,22720,59,1247,6530,4964,360,41,14063,710,314,142,176,9992,1513,103,4185,23,628,162,136514,41,6606,209,14,209063,142,70,1578,1844,396322,107,16340,56749,92,78,1459,513,209772,6689,153,93,66,306,1485,5588,10237,217,85,678,2602,7381,20819,18018,108,398,10,1420,859,46,5908,143,2404,6882,21773,26876,209508,28049,32,65,24838,240691,4023,14302,28158,40077,95,239,2055,114,9782,13040,10,105,6134,958,1699,16257,64,77864,1199,77380)
            osevenD <- c(43472,18756,99,51563,35833,3670,4539,25798,133,867,7176,5316,585,42,10578,658,861,105,174,4223,311,71,2769,18,1248,238,184669,45,8608,423,10,203539,196,76,1630,1858,350080,70,9110,42237,100,311,1982,345,238989,2446,150,80,16284,933,725,2851,18071,199,432,933,3171,3472,21135,21075,101,378,14,1722,964,23,18215,184,2183,10910,26606,8441,188453,18940,23,42,26311,404332,2614,16334,30875,20918,66,218,2396,65,51049,10145,10,103,3709,354,1106,16449,47,102950,1670,78849)
            oeightA <- c(45429,9490,144,65653,37338,3833,5462,34838,110,1335,230,5185,447,1081,23164,1002,7689,150,152,12146,221,168,3205,80,1059,98,173012,51,15722,398,14,249501,146,183,973,1607,564012,96,103756,81207,91,523,2948,555,225872,2492,185,174,69,16179,4829,3186,14680,191,1286,2069,2778,5864,24563,21663,52,436,10,3002,852,51,17508,220,5167,7995,35846,11062,144669,36686,45,41,21347,576128,2583,12849,41799,65420,37,191,2494,89,424066,6842,10,251,5238,617,621,19695,28,120913,2484,91944)
            oeightB <- c(53531,11648,135,114156,45069,3517,4352,41540,155,3338,339,6749,545,1416,23777,1781,7295,373,233,27362,170,124,6008,247,1116,170,207748,51,20064,530,20,352921,300,92,2434,3826,583019,139,38577,98730,75,281,2615,257,264838,3496,89,220,506,1137,2783,4327,12658,189,201,2518,3569,5944,31882,27120,71,617,10,2433,971,42,15034,221,2626,9485,24532,14941,255012,43795,75,32,25174,416833,2588,26150,50224,200746,65,263,1263,73,288487,10330,165,203,13597,514,1134,15045,71,123457,1939,84797)
            oeightC <- c(47839,12509,96,130401,43548,3140,3126,40116,93,1079,421,6152,666,628,25744,1081,28408,364,148,15042,267,60,3579,395,239,149,177438,56,17181,1609,64,264000,176,79,2026,2547,564916,137,22280,68993,96,308,1975,741,266661,2993,44,118,576,442,2722,3408,13723,270,341,3087,3131,4928,25902,30223,80,787,23,5283,865,50,5347,235,11030,8951,22290,11342,192368,28782,37,36,22906,395841,2195,29935,47877,12883,75,290,796,219,828869,8641,4.5,175,12770,1045,2640,21416,45,111478,5378,87505)
            oeightD <- c(48440,8912,117,78976,38758,3595,3224,34569,83,483,304,5001,434,203,24201,1407,5135,256,154,9237,284,92,3166,513,1290,149,139292,41,15816,282,24,236694,143,154,1080,1557,538035,94,38413,57710,84,616,2376,37442,242380,1742,97,224,43,632,7335,2831,20139,255,279,2711,2928,3913,21548,20016,120,775,18,6005,663,99,4382,126,15937,7491,13911,7914,167651,22477,41,23,17093,341653,2222,19165,41648,72151,56,263,313,95,862819,5673,10,433,8613,405,1016,32963,72,114831,6639,85083)
            tenoneA <- c(44708,62728,92,58229,33007,4557,10375,37949,117,1633,4725,5943,2722,157,21182,1465,334,89,195,14022,204,103,3936,18,2983,463,155984,51,12852,311,96,462019,301,92,2626,3499,391072,122,97872,76295,84,673,2012,570,315375,5662,247,1127,839,756,1207,6716,15961,188,306,1106,4157,16305,30301,38468,66,462,19,8332,1678,56,20318,623,1721,8213,63671,20757,203013,41659,50,50,34068,593673,2086,32499,47706,309242,66,244,3518,80,17134,11006,24,143,15288,753,2126,44296,68,122149,2197,107193)
            tenoneB <- c(38218,38039,109,44872,28686,4421,6669,31615,66,681,5636,5382,2154,103,19369,1830,1748,146,124,1145,1758,102,3471,28,1912,2509,124464,33,10672,371,70,398285,121,122,8512,11520,370299,344,50867,61848,123,525,2009,5262,288639,4415,77,259,44,786,3912,5490,13636,196,274,750,3346,13102,23932,27286,114,2104,9,7136,1052,69,8399,709,2204,6429,45491,16141,129410,44070,37,28,32911,378103,2066,32144,38051,133976,70,271,778,92,62964,10264,10,276,5267,1447,3047,11389,50,97487,1599,102574)
            tenoneC <- c(93509,39440,71,50214,31903,3954,4743,40617,122,1611,3444,6254,1732,108,21414,1341,227,151,315,10599,232,139,4473,32,3000,2211,132939,36,14150,445,122,378728,171,7537,2023,2641,483688,118,72076,85858,111,1005,2138,530,323840,3665,98,254,993,480,2496,5237,18612,229,297,1058,4146,8019,29422,32549,73,749,10,8091,1147,130,6278,361,2824,6860,48678,13957,142748,51039,50,56,34312,537789,2105,35657,47393,174469,80,234,643,119,56718,10118,10,306,9929,878,1828,11499,68,120460,2149,88911)
           tenoneD <- c(50586,39356,52,75803,33009,4393,8615,41686,171,1548,4396,5875,653,860,17134,1881,259,69,153,4697,330,129,6509,27,3202,848,184724,47,11053,2201,1473,406501,140,80,1978,2507,582602,181,74791,117048,104,912,2038,391,325208,6824,131,143,384,1142,2575,4716,17706,175,174,1073,3941,13752,22988,26556,65,840,19,14722,1052,47,7640,191,14647,9193,49290,20928,207596,42740,33,46,32420,260319,2675,36404,49403,140328,70,212,1090,124,1069388,12101,10,137,5231,1583,55839,33870,62,91496,5753,99473)
            oneoneA <- c(39607,16596,115,104639,6038,3587,5708,37989,521,1264,5631,681,405,89,22901,1401,1615,87,210,4487,1216,134,4308,33,2864,321,158659,42,10966,38532,10638,391147,178,93,2685,3576,481266,90,24336,63922,92,456,2762,596,301592,6285,183,123,392,1647,496,6132,12223,354,405,1552,2994,7902,22747,21083,90,400,4.5,5956,887,29,17496,387,10581,8802,28109,20883,247375,36178,46,32,23505,203967,458,36793,45463,18919,46,264,2387,825,415748,8880,10,96,3066,462,2437,67957,40,81342,2984,70497)
            oneoneB <- c(35272,16615,86,89212,8936,3788,4978,38414,4307,1626,5434,1905,558,54,22529,1796,248,134,177,14195,26463,164,2969,20,2840,227,155192,50,14717,554396,98587,348659,279,66,3169,7101,525439,100,57840,60407,215,748,3054,334,308026,5512,143,87,1935,822,1330,6326,17064,235,28040,1725,3133,9602,18269,20572,70,2842,27,4460,955,52,6303,190,2157,8962,38125,22208,195954,35451,23,36,24996,234453,1509,26998,44589,12394,103,274,1185,3497,167017,10062,14,128,4013,284,888,74248,69,115321,2591,67191)
            oneoneC <- c(39576,20198,111,72943,9090,3865,4766,39003,779,1060,7171,804,405,128,17427,1215,217,128,241,14963,3416,124,3232,18,2967,166,149117,36,12666,66058,18574,307486,333,70,1948,1917,451509,119,42583,51094,76,1389,3308,374,288913,3936,121,267,2149,871,2540,4698,21056,313,4555,1439,2915,6800,22820,32870,166,454,65,5089,905,30,15850,229,1629,8741,21142,13913,253768,32690,37,37,24016,223297,1666,29029,46590,24046,52,194,1013,3056,68519,9820,10,249,13245,1298,2093,120037,68,97670,1696,83957)
           oneoneD <- c(38280,14589,93,46977,8335,4003,8628,33378,135,1510,4099,783,340,61,24025,1889,431,113,257,3718,289,131,3905,477,3799,120,83698,69,11139,2689,1076,385329,90,88,2187,3054,506252,133,33177,66308,74,778,3085,636,277946,6512,135,139,53244,331,2738,5519,21104,239,421,1204,2680,11024,19636,14683,114,428,24,5010,856,33,7259,419,1950,5597,34996,18002,165386,43747,32,74,25989,172832,1643,28131,40841,26239,70,253,1835,183,80600,8506,10,213,3415,1852,995,103896,18,75781,1629,91796)
           onetwoA <- c(38180,10186,139,29220,33111,4038,3367,29273,67,720,4788,3992,482,36,16490,954,1409,392,14543,12421,250,73,2874,18,1640,137,167296,36,12193,310,30,193077,260,80,798,1147,462952,104,45592,71862,166,191,2040,394,246272,2688,116,144,26527,245,748,3453,11418,271,222,3077,3048,5563,21466,27374,129,602,10,2648,949,34,7376,203,2426,7789,21153,10895,269684,30996,33,27,25585,310808,2336,12306,36593,53576,94,239,663,125,109659,8358,10,79,4483,616,1004,19334,41,85693,1386,65024)
            onetwoB <- c(42105,15536,63,28079,28068,3962,4890,39054,118,1364,8705,3848,467,72,15135,1136,1365,102,224,16517,262,137,3378,42,1802,157,171212,70,11726,328,20,286238,212,80,3432,4486,366649,155,43264,56550,110,130,1797,323,273048,3991,155,118,3466,480,589,4636,9504,264,9677,1305,3786,7419,23855,34294,100,747,10,2872,854,47,6565,143,2659,8230,33914,14235,289203,29091,23,70,25262,419294,3150,31383,45458,60525,97,215,447,97,29583,9902,32,97,7507,489,2715,14283,24,100461,1507,86390)
            onetwoC <- c(72152,12842,109,33906,29256,3566,5191,35558,105,1087,7472,4433,1890,122,20088,1337,1795,275,305,13915,156,131,5132,52,2349,175,146364,36,12675,445,20,217115,177,90,2622,3622,459552,202,124293,81726,91,577,2986,262,299121,4383,84,58,405,1890,2160,3847,24247,230,1634,2241,3978,6782,23290,21557,134,2411,18,2676,1254,19,6613,1261,2460,5662,31545,14220,426332,36422,27,47,29868,370810,2384,37037,43500,43445,89,248,341,102,46000,9875,65,157,3740,1190,2839,21164,46,90738,2174,66780)
            onetwoD <- c(60382,14114,62,26309,28167,3913,4841,39828,104,1418,5205,4030,381,675,23510,1076,907,168,161,16521,165,110,3634,46,1617,236,175956,51,13068,519,245,331554,162,136,3036,3906,429025,86,54040,99376,68,235,3200,335,284881,4145,43,279,467,6303,765,4848,16187,250,353,961,3644,7459,19772,21236,58,579,10,2946,1363,59,5399,2086,1994,6985,27231,16442,504260,43940,37,51,30060,325599,2452,42681,46788,15820,55,234,441,151,38463,9230,57,150,3762,353,4570,19752,75,89541,1863,86249)
onethreeA <- c(42007,12755,14301,35274,32120,4189,6994,35938,168,1756,5458,2710,435,38,8872,1331,167,148,303046,12775,646,163,3751,23,1677,174,120096,33,11962,278,183,205949,20593,83,836,1327,334860,124,66586,75044,85183,83,2572,510,289358,5471,170,101,25028,15676,493,4628,8875,187,2905,2148,3747,8912,19277,16716,63,490,18,5124,997,47,13551,237,4521,6844,35333,20808,307433,18341,27,51,22265,471017,2025,20533,42926,13560,74,213,415,141,281351,7187,65,155,2740,885,1798,39107,74,107676,2066,80973)
            onethreeB <- c(37958,18050,13542,34872,30758,4450,4221,37840,87,2285,7364,3495,368,153,10355,1286,162,104,2285,11665,255,150,3898,20,462,177,153062,55,11461,316,29,271691,4045,80,2860,3555,410944,133,31130,86262,107367,81,2851,3193,286407,7175,197,73,71,2330,600,5958,9331,291,376,1236,3936,11570,20089,24076,95,294,28,5066,1044,56,17145,92,3540,7670,34722,24228,339162,21368,28,33,22936,353176,2173,18698,45030,9292,113,208,485,66,234593,8624,46,86,8454,371,2200,10140,72,109606,2269,85960)
            onethreeC <- c(77239,19266,13480,43560,45054,3820,4400,45782,78,1176,5604,5069,2855,132,10488,1480,105,173,232,19306,160,2570,3441,19,734,207,171712,37,8236,236,19,370730,309,74,3493,5304,424461,97,13835,81836,106065,156,1549,305,303968,8760,84,113,365,4745,512,6901,9324,241,4180,17154,3734,15172,20117,17245,61,2664,32,8151,842,1198750,5116,467,2773,7368,49063,26876,550377,27274,153,75,25824,420630,2048,27234,55875,68757,103,234,464,181,113762,7572,2675248,84,7296,2197,1591,19392,695672,86164,2704,79114)
            onethreeD <- c(43518,13902,12308,49505,41829,3653,3325,32057,127,2182,5964,4472,566,158,10266,638,159,94,155,4338,291,68,4381,14,495,125,143148,41,12673,232,24,280065,210,69,3352,3959,291649,130,17471,52484,102940,79,1612,321,275680,5851,131,146,5319,2316,343,5389,7076,208,2702,1029,3414,9023,18668,18985,91,2194,9,4383,741,181,4729,238,10272,7265,31835,20310,144690,24108,18,37,25251,407226,2162,16677,39711,4995,80,290,322,79,353330,7242,400,74,5854,1037,1751,13546,120,116074,2251,74325)
            onefourA <- c(54576,12613,95,81918,45438,4290,5462,36046,167,1540,5487,5186,574,144,15928,923,1631,191,113,41508,134,114,4447,104,248,145,167196,46,14182,245,24,294090,177,69,1460,1683,454998,79,43640,103577,84,379,2215,529,260740,4868,136,193,786,1244,2544,5949,14614,241,140,2406,3845,6195,24547,25425,94,621,10,6855,1147,241,6895,195,7744,7096,19874,20376,431804,32698,23,46,20215,402537,3330,24170,42896,8589,47,208,726,159,424563,7608,726,144,7544,642,1078,39609,72,87347,3470,82345)
            onefourB <- c(43019,9831,102,65800,38298,3806,5093,28993,107,1696,4654,4546,601,32,15481,804,518,386,140,27970,314,110,5187,18,133,155,115051,45,12529,277,10,219732,163,79,7211,7745,421042,160,25643,138159,99,479,2049,904,240354,4558,158,148,40,634,847,4621,19438,211,273,3014,2719,8057,18726,19235,75,628,23,7883,907,65,7179,161,13500,6620,18578,19885,181820,35462,28,50,25200,387449,3120,11602,34632,56016,52,262,882,123,676068,7653,105,99,10914,1273,1091,27113,50,97256,7103,80932)
            onefourC <- c(56230,13292,79,100751,40633,4011,6817,37035,73,1738,3137,5392,418,3500,25986,1263,371,142,180,18558,175,132,4945,28,369,110,135518,41,13181,195,10,414605,294,131,2757,3215,455527,133,24458,98159,78,496,2061,443,282560,7864,111,108,955,4126,534,8304,16430,192,184,2012,4107,10649,24308,21251,107,440,10,5243,1426,60,14861,81,2558,7151,24088,34753,291253,51639,32,36,30097,301466,3101,4436,44924,37815,122,325,665,88,104640,8544,20,90,5402,1496,1653,27061,110,100521,2176,68272)
            onefourD <- c(45873,11797,137,65792,40027,4217,7512,38006,128,1489,5808,4927,438,3915,17919,1934,317,185,194,40137,296,120,4691,18,136,82,115780,55,11718,260,20,243800,325,102,2484,2489,465230,140,31092,115885,102,506,2704,494,276832,4287,137,208,667,5486,548,4983,17673,177,669,1405,3741,6375,23503,22513,105,510,24,5156,1078,56,17186,235,2680,6136,26244,18688,431521,34068,46,47,25417,374171,3592,20027,45086,40486,98,180,1028,118,92918,7486,14,73,14351,1198,596,11186,50,96353,2122,82208)
            onefiveA <- c(47874,15818,130,83529,32219,3583,7660,36096,104,1354,8828,4544,458,112,35606,1169,545,212,276,9951,291,86,3975,23,2974,79,87603,46,12652,483,223,484646,327,80,1048,1509,507110,131,102847,76602,96,191,2767,553,280826,7931,99,184,4852,918,513,7684,10986,229,241,1392,3738,13118,22210,20504,104,1676,9,2434,1369,33,15121,214,6944,4522,41735,30848,61453,53854,23,56,33811,246527,2041,27968,43225,71778,111,219,1110,184,479999,10472,10,80,4420,7514,978,19366,44,97994,3055,73301)
            onefiveB <- c(52925,12399,108,81321,30818,3754,4290,41477,120,2690,6248,4699,678,94,26710,993,770,311,231,13172,193,109,6222,28,1821,132,116336,41,14349,518,10,301524,216,71,1487,1808,578411,130,45446,102958,80,508,3053,448,272561,5689,99,125,461,783,423,5339,20849,208,249,2971,3954,9301,19643,19807,118,1279,10,3145,1234,33,15378,206,4204,6666,25029,23575,285475,45129,37,64,27586,641408,823,30522,50342,14290,60,205,528,117,580018,10222,19,66,7054,1463,2675,40198,48,106639,7888,59548)
           onefiveC <- c(51387,15765,118,83077,33316,3444,8086,35898,102,2556,6453,4557,752,255,37792,866,101,5896,210,12636,120,231,5006,23,1687,144,167442,42,12503,228,30,635883,299,112,2330,2787,487295,112,82062,97504,95,405,2950,601,301654,10562,110,156,661,584,496,11401,16815,193,278,2014,3452,24889,21643,18918,111,601,9,1454,1050,20,15680,172,2201,6602,42019,52515,660321,81259,32,41,46733,552320,2324,27969,43591,10259,75,238,818,196,156458,16883,9,84,2223,854,4701,13473,62,92530,2098,69949)
           onefiveD <- c(42892,15829,139,73256,29866,3554,5411,33509,94,2760,9102,4181,573,299,22875,791,775,199,263,15615,222,118,4734,23,2304,170,116004,42,16258,205,44,337964,157,72,1433,1885,443420,99,74270,93929,88,806,2540,513,254301,3880,221,112,11355,920,394,5739,21513,167,412,1383,3808,9031,20973,25964,104,825,10,2582,1039,47,19774,296,6590,7431,38936,18341,374282,43984,37,32,30474,357745,2294,28804,41049,11916,51,274,2358,96,459660,10519,10,64,4029,991,1043,20482,68,112713,2661,79119)
            onesixA <- c(54392,30203,109,70562,34021,3172,4664,32104,83,3300,4098,4778,460,277,23054,1807,81,266,129,15021,90,94,3713,29,3142,127,167850,37,13945,368,10,369514,198,93,1563,2003,463278,122,65240,67999,128,424,2951,531,319202,4863,99,210,541,947,669,4048,13747,211,242,2610,3936,8222,18730,15800,82,584,10,8404,1075,57,15138,128,2382,8760,32211,16133,439140,50749,48,50,23796,315510,2818,10863,38386,16806,56,240,923,199,87033,13112,19,107,6123,857,2234,41402,36,70317,1905,86340)
            onesixB <- c(42262,23543,83,50076,29360,3461,4420,23750,61,3050,3460,3464,391,60,21912,991,98,114,127,11963,351,94,2666,28,2916,157,124124,55,11823,319,10,395518,139,64,43787,48278,404702,96,107341,46214,152,212,1744,264,261997,4692,193,237,60,336,182,4874,14216,198,1538,1000,2720,11074,14563,12869,87,287,18,8912,896,29,17581,350,18503,8099,46018,14308,340920,48079,45,33,23800,281091,3052,8162,29103,47135,70,291,1880,156,562422,10867,14,74,5316,678,1986,31637,44,58764,5124,97786)
            onesixC <- c(48341,32865,63,65044,29926,3705,4162,37012,68,4115,3472,5020,758,126,24963,1902,101,449,219,11313,103,83,4091,14,3978,131,159796,37,18060,321,14,428778,315,354,3605,6499,439925,87,65500,61727,120,259,2140,469,331327,3994,89,104,513,54808,273,3883,16543,245,661,3045,3741,8063,21541,16866,78,686,14,9504,973,523,4211,196,1715,7672,27197,16362,537403,50737,27,27,24199,343925,2247,11479,44355,127009,98,179,317,124,158040,12910,2547,84,4257,661,2143,40114,1099,78033,1962,86103)
            onesixD <- c(53968,30165,88,65734,29987,3911,4559,27775,88,2157,5240,4161,379,162,30351,1372,93,761,301,25033,290,67,3056,131,2424,179,151955,45,11640,288,24,452142,168,81,1844,2609,577571,120,60180,111154,90,175,1991,426,310033,4807,117,205,2337,297,336,5023,12060,197,474,1332,3220,12685,15617,11661,268,1931,20,10216,718,37,15376,198,962,9985,40796,19076,205067,71450,36,38,32548,184347,2224,23710,34121,34777,80,335,606,425,127245,13101,10,151,4632,1608,2012,57348,85,72582,1720,98442)
            onesevenA <- c(36460,85293,62,56905,26445,4285,8773,40239,3352,1346,9198,4476,490,51,17639,2145,387,85,262,10520,23292,10084,4545,20,108,101,94821,55,11775,440103,127076,330938,253,73,1898,2840,535433,185,341243,140700,79,408,2269,450,289105,8428,261,205,1035,1158,493,7637,11684,197,174,691,3475,21570,22826,37695,52,760,10,3659,1353,51,15071,1119,1839,6426,74204,34954,204008,44525,19,27,39814,574959,2761,58959,47513,37459,56,253,1068,917,294884,10450,10,65,5987,6634,1683,8418,31,77879,2134,117973)
            onesevenB <- c(42936,20995,95,49962,35859,3936,2503,38164,799,600,9893,4464,581,118,13819,2026,1198,90,292,11648,1879,2617,2949,27,72,140,148297,41,10785,50816,20194,172356,274,60,947,1497,455745,115,73624,61106,58,231,2732,431,260520,1699,132,236,570,940,357,2185,14180,241,392,630,3276,3031,19160,21121,91,1702,10,3796,1010,33,14080,113,6912,8839,24795,5794,189400,27325,36,23,28742,346986,2027,36563,45196,10280,63,162,751,788,565939,10134,9,65,5093,1052,868,16683,74,82151,3348,103992)
            onesevenC <- c(64672,70585,113,50860,9622,4230,6486,39383,3437,1297,8456,1945,761,620,25722,1952,810,105,277,14317,10291,9722,5710,18,157,194,158837,51,16266,392962,97016,486257,154,79,2566,2972,566115,99,335056,159131,85,306,2639,597,321619,6836,214,183,215,494,496,8306,12643,240,253,1057,3888,11796,27610,51505,76,867,10,3025,1476,89,13857,976,604,7751,63367,29027,593821,61028,55,42,40980,456955,3203,58486,48005,37534,46,216,786,1524,138312,13394,303,55,9874,835,2787,51872,60,65359,1873,98560)
            onesevenD <- c(44368,58937,107,70757,9721,4294,7715,33819,2316,2151,8589,1880,640,103,32638,2306,501,162,267,20378,2883,7260,3616,9,86,129,141800,46,12268,91613,39886,602726,222,46,2214,2983,558944,96,437937,136434,73,266,2508,454,330826,11607,313,229,334,5693,445,12506,10618,191,2630,747,3042,24233,23904,30039,69,668,18,6510,1172,55,18544,684,5835,7235,93666,48135,592971,84887,18,32,54830,413250,2988,55498,41866,4723,63,216,2668,6134,781292,14541,10,120,8146,1009,2382,14334,51,66303,4434,101993)
           onenineA <- c(41600,10022,105,57102,7220,3553,8975,28296,97,1258,3698,707,386,193,20438,948,514,127,307,7786,332,108,3330,50,513,115,137182,37,11351,451,20,344741,190,98,2418,3101,388641,105,47436,51453,111,120,1385,362,207180,8385,132,125,60,29244,239,6881,6471,227,1923,705,2479,16346,16596,11152,48,1741,4544,2011,694,10,9317,228,4587,6287,40356,33431,408947,42718,23,36,28224,408728,5195,16034,34111,20042,35712,195,444,82,279521,9425,4.5,113,2716,951,4579,6845,51,82285,3813,71353)
            onenineB <- c(87963,13736,118,78640,8509,3980,8195,43820,71,1842,6530,1067,454,471,26329,1964,389,166,187,15604,145,115,3458,19,2137,116,163242,27,18910,223,10,328738,191,65,786,1009,523908,125,133135,91540,113,143,2523,312,272701,9602,121,140,421,20571,243,8788,8068,199,228,1744,3780,18506,19395,17936,56,610,14,2277,595,50,15886,233,1186,6792,54580,43369,535089,57991,14,41,33548,452631,5184,33802,51937,2948,46008,247,390,87,135656,11867,10,66,4669,944,999,33165,55,106484,2309,77761)
            onenineC <- c(70475,13366,110,77438,8321,3067,8063,34055,56,2268,3674,962,523,174,26135,1163,351,144,152,11523,102,115,4099,23,1630,146,196867,42,16903,224,10,393590,265,52,1800,1967,489861,124,81765,94333,112,205,2620,643,269376,6223,85,122,610,891,356,6824,10310,290,263,915,3317,14152,20016,16552,89,821,4895,2014,651,55,7360,260,1067,7216,68358,28571,576513,62798,18,27,39590,841076,5709,25718,43076,28332,58557,221,390,65,28412,11823,32,71,5161,464,2718,20879,72,88652,2198,73885)
            onenineD <- c(65541,11805,109,68684,7515,3478,7349,34263,81,1564,4230,765,563,3939,24956,1032,435,99,175,3253,190,102,3935,4.5,1475,155,148113,27,14037,206,14,393953,319,176,1386,2242,451811,169,60838,80364,109,118,2294,679,235898,6786,54,80,464,11005,207,6549,7599,165,347,863,3111,15512,18307,14100,53,1732,2184,3922,640,60,5923,247,10605,7525,47980,22985,356316,60536,36,32,36120,631081,5061,28472,41112,32033,35536,224,344,77,574943,9818,10,66,2092,3380,2139,14856,60,91620,3668,72013)
            twooneA <- c(48429,10340,98,77837,7542,3345,2743,54918,168,1601,7939,807,575,163,18191,1205,346,165,169,3559,215,129,4290,18,92,122,187044,32,13776,484,53,252850,270,85,1381,1877,508579,94,2001,62640,88,289,2776,2631,271226,4715,80,165,895,285,492,3740,8965,206,819,2498,2998,8182,20764,17423,63,1608,10,7334,825,61,7620,385,12103,8074,13447,18058,649764,31255,28,18,28229,435966,2275,20420,63871,154113,47,314,757,60,608732,11381,24,65,4578,339,2681,9729,78,103789,3506,64055)
            twooneB <- c(42723,10406,105,58901,6559,3659,6773,51088,93,1951,9694,676,495,678,20489,780,585,154,210,3290,1600,97,4119,27,140,115,183606,46,11764,379,30,312908,244,135,2317,2484,446900,144,1760,72518,110,181,2173,787,235202,5742,92,131,65,586,359,4701,6065,228,217,1343,2556,11737,17866,16982,56,1952,18,5209,791,37,16391,282,1667,7175,33678,22142,366230,36980,27,23,27068,438658,2415,15096,60392,22052,72,276,1104,98,219943,9642,19,70,4180,776,968,7729,34,87116,1672,73993)
            twooneC <- c(51806,12238,102,66456,7459,3192,4987,51114,119,1038,6971,887,644,3552,20033,1258,235,183,258,15310,146,74,3866,23,110,185,168673,46,14971,508,98,315722,144,81,1636,2094,426049,150,1454,63261,75,268,2955,929,282150,5952,89,304,313,1049,280,5210,10972,241,5608,2502,3383,10255,23527,17450,88,642,20,5100,890,117,16046,304,687,5902,19708,27232,481637,34068,27,32,28527,478837,1992,9746,61443,103354,60,208,432,103,55795,10181,369,130,3822,4844,850,24806,69,107982,1736,62523)
            twooneD <- c(44905,11674,81,73840,7457,3498,7344,57891,52,1939,6971,811,838,4946,28559,870,717,177,208,12893,124,116,3564,23,130,153,163654,41,12019,294,10,389281,222,86,1633,2007,528211,105,2089,94933,98,236,2910,2192,275529,9646,208,156,428,277836,1538,6663,9006,203,179,977,2861,18302,19668,16636,80,838,10,6383,1233,39,27168,268,738,8439,30954,37380,541354,55757,37,32,43440,438522,2267,23090,67850,25388,103,220,3612,62,44693,16661,10,133,2868,481,1133,8384,54,95948,2077,71754)
            twothreeA <- c(48030,14978,115,75829,7634,3795,4149,31741,100,1620,2435,640,299,181,23219,1601,578,286,246,14030,358,142,4880,23,630,166,151352,33,11754,269,30,307294,288,82,723,890,371693,153,86949,66072,185,178,2775,570,258158,3736,107,177,8268,685,1439,3794,12274,214,195,3622,3282,7063,22781,31318,63,2062,9,4904,866,32,19625,714,25655,6972,20582,13708,155888,29186,32,41,15815,234255,620,22363,38751,21595,46,436,2265,97,743348,5932,14,130,3597,329,3263,22751,38,94802,4643,63014)
           twothreeB <- c(50820,12279,111,88872,8435,3718,5788,39779,133,1093,6068,832,535,243,16494,1940,426,274,169,10681,247,88,4533,18,458,94,163517,41,13848,214,20,264974,158,77,2119,2180,420477,143,152741,89823,79,152,2801,571,288440,3328,164,217,591,786,600,3308,12442,183,126,2351,3645,8030,22292,21137,57,234,10,3969,977,33,18415,548,6803,5906,17291,12725,622792,29018,9,32,18612,357251,1696,21462,47821,2918,74,194,1468,84,632517,5734,10,66,2172,462,591,29489,77,85816,2593,73359)
            twothreeC <- c(36604,10496,126,42359,7235,3972,6138,28430,71,1281,3606,549,524,46,18556,2469,396,191,206,13153,377,84,4842,28,1207,136,116599,42,11814,388,20,259081,210,85,1032,1041,376001,161,95732,65750,88,274,2784,3215,258117,2504,93,113,93,584,305,3253,12565,150,221,2312,3285,5201,22788,19001,90,613,28,1889,801,44,8892,868,2173,5049,20042,9059,555316,31249,51,51,21291,448261,1655,11805,34687,8965,74,187,465,170,211753,7830,4.5,70,4427,708,1694,13016,114,83220,1892,61330)
            twothreeD <- c(46655,12320,58,76458,7671,3455,8106,36670,83,1096,6333,719,419,94,17013,2311,1157,119,196,19321,250,91,8054,32,1210,213,127693,55,13652,403,51,292279,352,56,8852,12343,513768,128,100200,114185,126,211,2824,410,283964,3180,57,145,1784,1680,336,3343,11071,286,367,1328,3150,8849,18291,24314,96,1884,14,2212,1332,33,17057,447,1145,6014,24669,13095,513330,31200,32,23,20232,446976,1616,24982,43964,20755,52,217,700,121,286417,5635,10,93,4591,960,2967,23208,42,89510,2069,76472)
           twofourA <- c(43674,11627,114,46715,6310,3632,5176,28682,96,638,3863,649,344,393,18547,1179,412,161,198,10232,1438,116,4160,19,1755,112,136210,60,10858,1219,369,385356,226,78,2427,3232,380462,136,2144,55953,91,203,2349,540,238700,4548,138,124,50,228,1918,4771,8439,198,458,1345,2306,11705,17803,19443,75,316,10,6911,647,20,17491,326,1678,6850,28806,16346,548725,43064,38,36,28585,417636,3365,11006,33961,147224,56,212,710,69,145126,8009,20,174,4632,836,819,39329,37,76771,1417,91415)
            twofourB <- c(50092,13853,98,64982,7102,3758,3884,34219,134,1434,3022,684,470,658,21928,997,481,215,129,4530,258,92,4947,108,612,170,169109,45,16711,661,148,238990,256,110,2934,3712,398923,92,11065,57154,115,297,3150,869,278601,3255,93,115,867,1882,1760,4156,19042,162,247,2681,2808,8265,19388,20114,79,2448,18,8510,717,49,15964,251,8270,6937,27278,13038,556244,43153,23,33,34185,557528,3120,17985,40538,128340,67,243,535,94,514841,12859,4.5,159,3846,1438,1892,4787,54,117494,3281,83945)
            twofourC <- c(50216,16274,82,56302,6349,3788,4355,28766,140,2786,4430,639,344,70,14969,919,1068,186,358,4484,415,94,3506,23,1564,176,149681,32,14844,1329,467,337570,326,69,1086,1693,337217,170,28080,50319,96,104,2380,587,254474,2811,120,170,17071,1319,4694,3856,12209,266,144,1878,2553,7179,21262,28780,61,417,14,7105,560,29,16568,286,1562,7322,29047,10141,510224,34820,28,32,26568,491020,3342,18085,35844,103755,80,211,698,77,63594,9330,23,514,2636,873,2524,23983,19,114664,1503,91055)
            twofourD <- c(61310,16963,96,70172,6990,3529,11977,35597,87,1265,5479,648,577,507,17325,1390,651,217,227,10758,168,51,6275,64,570,133,213538,32,13973,951,217,294423,178,50,3275,3574,452687,97,21567,64585,88,128,2560,6081,270416,4956,109,169,312,557,11849,4169,9706,171,191,2498,2966,9466,22389,26295,85,2198,4.5,10611,618,97,17979,430,17616,7162,85641,15058,697090,39662,32,23,29291,474418,5099,24144,42256,131451,85,215,732,79,680220,9235,9,946,4354,240,3079,9608,42,99554,5038,94318)

x <- data.frame(ooneA,ooneB,ooneC,ooneD,otwoA,otwoB,otwoC,otwoD,othreeA,othreeB,othreeC,othreeD,ofourA,ofourB,ofourC,ofourD,ofiveA,ofiveB,ofiveC,ofiveD,osixA,osixB,osixC,osixD,osevenA,osevenB,osevenC,osevenD,oeightA,oeightB,oeightC,oeightD,tenoneA,tenoneB,tenoneC,tenoneD,oneoneA,oneoneB,oneoneC,oneoneD,onetwoA,onetwoB,onetwoC,onetwoD,onethreeA,onethreeB,onethreeC,onethreeD,onefourA,onefourB,onefourC,onefourD,onefiveA,onefiveB,onefiveC,onefiveD,onesixA,onesixB,onesixC,onesixD,onesevenA,onesevenB,onesevenC,onesevenD,onenineA,onenineB,onenineC,onenineD,twooneA,twooneB,twooneC,twooneD,twothreeA,twothreeB,twothreeC,twothreeD,twofourA,twofourB,twofourC,twofourD)                      
x
sample <- c("Egg-101-A","Egg-101-B","Egg-101-C","Egg-101-D","Egg-102-A","Egg-102-B","Egg-102-C","Egg-102-D","Egg-103-A","Egg-103-B","Egg-103-C","Egg-103-D","Egg-104-A","Egg-104-B","Egg-104-C","Egg-104-D","Egg-105-A","Egg-105-B"	,"Egg-105-C","Egg-105-D","Egg-106-A","Egg-106-B","Egg-106-C","Egg-106-D","Egg-107-A","Egg-107-B","Egg-107-C","Egg-107-D","Egg-108-A","Egg-108-B","Egg-108-C","Egg-108-D","Egg-110-A","Egg-110-B","Egg-110-C","Egg-110-D"	,"Egg-111-A","Egg-111-B","Egg-111-C","Egg-111-D","Egg-112-A","Egg-112-B","Egg-112-C","Egg-112-D","Egg-113-A"		,"Egg-113-B","Egg-113-C","Egg-113-D","Egg-114-A","Egg-114-B","Egg-114-C","Egg-114-D","Egg-115-A","Egg-115-B"		,"Egg-115-C","Egg-115-D","Egg-116-A","Egg-116-B","Egg-116-C","Egg-116-D","Egg-117-A","Egg-117-B","Egg-117-C"	,"Egg-117-D","Egg-119-A","Egg-119-B","Egg-119-C","Egg-119-D","Egg-121-A","Egg-121-B","Egg-121-C","Egg-121-D"		,"Egg-123-A","Egg-123-B","Egg-123-C","Egg-123-D","Egg-124-A","Egg-124-B","Egg-124-C","Egg-124-D")
z <- data.frame(sample)
z
```
3. I have already removed all of asked data in the first step.
4. There are total 98 features, with 95 features having no missing value; one has one missing value; one has four missing values; one has eight missing values. No feature has more than 25% missing values.
5. Print first 6 rows of the feature and sample data.frame. And print the first 6 rows and first 6 columns of the numeric concentration data.frame. Also print out the dimensions of each data.frame.
```{r}
z[1:6,]
y[1:6,]
x[1:6,1:6]

